---
title: "Case-Study"
author: "Jingyi"
date: "10/20/2019"
output: html_document
---

This example is based entirely on live-coding and uses the NYC Airbnb data. The data can be imported using the p8105.datasets package:
```{r}

library(p8105.datasets)

data(nyc_airbnb)

library(tidyverse)

```

As always, I’ll do today’s coding in a R Markdown file, sitting in an GitHub Repo / R Project.

## Understanding variables

First, let’s take a few minutes to understand the dataset and the variables it contains.

```{r}

# View(nyc_airbnb)
str(nyc_airbnb)

nyc_airbnb %>%
  count(room_type)

nyc_airbnb %>%
  count(neighbourhood_group)

```

## Brainstorming questions

A major element of data science is to ask questions, and this dataset provides some rich opportunities. For example, we might ask:

Does rating vary by neighborhood, room type, or both?
How is price related to other variables?
Where are rentals located?
We’ll take a few minutes as a class to brainstorm some additional questions, and then try to answer some of them.